Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-19 WSSSPE3/report/wg_appendix_industry_interaction.tex
fixed quotation marks

Our initial broad question was, "What makes for successful transitions of scientific software from academia to industry?" There are a number of potential funding transitions that may occur:  
%
\begin{itemize}

>>>>

Our initial broad question was, ``What makes for successful transitions of scientific software from academia to industry?'' There are a number of potential funding transitions that may occur:  
%
\begin{itemize}
